### 2017-10-03 manuscript.Rmd
correct references

Psychologists should be able to falsify predictions. A common prediction in psychological research is that an effect exists in the population that differs from zero. For example, we might predict that priming American Asian women with their Asian identify will increase their performence on a math test compared to women in the control condition who are primed with their female identity. To be able to falsify this hypothesies, and design a study that allows for strong inferences @platt_strong_1964, it is important to specify which test result would *disprove* the hypothesis.

@@

Even though equivalence tests are just a small variation of traditional Frequentist tests (testing against the SESOI, instead of 0), their use was limited until the availability of user-friendly software to perform the calculations (@lakens_equivalence_2017). In this article, we discuss different approaches to determining the SESOI for psychological research, and provide detailed reproducible examples of how to perform power analyses when designing equivalence tests, and statistical re-analyses of published psychology experiments.

@@

An objectively determined SESOI should be based on quantifiable theoretical predictions, such as computational models. Sometimes, the only theoretical prediction is that an effect should be noticeable. In such circumstances, the SESOI can be set based on just noticeable differences. For example, Burriss and colleagues (2015) examined whether women displayed an increase in redness in the face during the fertile phase of their ovulatory cycle. The hypothesis was that a slighly redder skin signals greater attractiveness and physical health, and sending this signal to men yields an evolutionary advantage. This hypothesis requires that the increase in redness can be detected with the naked eye by men. @burriss_changes_2015 collected data from 22 women and showed that there was indeed an increase in redness of the facial skin of woman during their fertile period. However, this increase was not large enough to be noticeable with the naken eye by men, thus falsifying their hypothesis. Because the just noticeable difference in redness of the skin can be measured, it is possible to objectively establish the SESOI.

>>>>

Psychologists should be able to falsify predictions. A common prediction in psychological research is that an effect exists in the population that differs from zero. For example, we might predict that priming American Asian women with their Asian identify will increase their performence on a math test compared to women in the control condition who are primed with their female identity. To be able to falsify this hypothesies, and design a study that allows for strong inferences [@platt_strong_1964], it is important to specify which test result would *disprove* the hypothesis.

@@

Even though equivalence tests are just a small variation of traditional Frequentist tests (testing against the SESOI, instead of 0), their use was limited until the availability of user-friendly software to perform the calculations [@lakens_equivalence_2017]. In this article, we discuss different approaches to determining the SESOI for psychological research, and provide detailed reproducible examples of how to perform power analyses when designing equivalence tests, and statistical re-analyses of published psychology experiments.

@@

An objectively determined SESOI should be based on quantifiable theoretical predictions, such as computational models. Sometimes, the only theoretical prediction is that an effect should be noticeable. In such circumstances, the SESOI can be set based on just noticeable differences. For example, Burriss and colleagues [-@burriss_changes_2015] examined whether women displayed an increase in redness in the face during the fertile phase of their ovulatory cycle. The hypothesis was that a slighly redder skin signals greater attractiveness and physical health, and sending this signal to men yields an evolutionary advantage. This hypothesis requires that the increase in redness can be detected with the naked eye by men. They collected data from 22 women and showed that there was indeed an increase in redness of the facial skin of woman during their fertile period. However, this increase was not large enough to be noticeable with the naken eye by men, thus falsifying their hypothesis. Because the just noticeable difference in redness of the skin can be measured, it is possible to objectively establish the SESOI.
